\begin{center}
    \addcontentsline{toc}{section}{СПІС КРЫНІЦ}
    \section*{СПІС КРЫНІЦ}
\end{center}

\begingroup
\renewcommand{\chapter}[2]{}%
\begin{thebibliography}{30}

    \bibitem{DBLP:journals/corr/CadenaCCLSN0L16}
    Simultaneous localization and mapping: Present, future, and the robust-perception age. /
    Cesar Cadena, Luca Carlone, Henry Carrillo, Yasir Latif, Davide Scaramuzza,
    Jos{\'{e}} Neira, Ian D. Reid, and John J. Leonard. //
    CoRR, abs/1606.05830, 2016.

    \bibitem{Li2016RealtimeSL}
    Real-time simultaneous localization and mapping for uav: A survey. /
    Jiaxin Li, Yingcai Bi, Menglu Lan, Hailong Qin, Mo Shan, Feng Lin, and Ben M. Chen. //
    2016. - Mode of access: \verb|http://www.imavs.org/papers/2016/237_IMAV2016_Proceedings.pdf|.
    - Date of access: February 2018.

    \bibitem{Forster2014ICRA}
    SVO: Fast semi- direct monocular visual odometry. /
    Christian Forster, Matia Pizzoli, and Davide Scaramuzza. //
    In IEEE International Conference on Robotics and Automation (ICRA), 33(2):249-265, 2014.

    \bibitem{murTRO2015}
    ORB-SLAM: a versatile and accurate monocular SLAM system. /
    Montiel J. M. M. Mur-Artal, Ra\'ul and Juan D. Tard\'os. //
    IEEE Transactions on Robotics, 31(5):1147–1163, 2015.

    \bibitem{murORB2}
    ORB-SLAM2: an open-source SLAM system for monocular, stereo and RGB-D cameras. /
    Ra\'ul Mur-Artal and Juan D. Tard\'os. //
    IEEE Transactions on Robotics, 33(5):1255–1262, 2017.

    \bibitem{engel14eccv}
    LSD-SLAM: Large-scale direct monocular SLAM. /
    J. Engel, T. Sch\"ops, and D. Cremers. //
    In European Conference on Computer Vision (ECCV), September 2014.

    \bibitem{sturm12iros}
    A benchmark for the evaluation of rgb-d slam systems. /
    J. Sturm, N. Engelhard, F. Endres, W. Burgard, and D. Cremers. //
    In Proc. of the International Conference on Intelligent Robot Systems (IROS), Oct. 2012.

    \bibitem{288}
    Ros: an open-source robot operating system. /
    Morgan Quigley, Ken Conley, Brian P. Gerkey, Josh Faust, Tully Foote, Jeremy Leibs, Rob Wheeler, and Andrew Y. Ng. //
    In ICRA Workshop on Open Source Software, 2009.

    \bibitem{Klein:2007:PTM:1514339.1514363}
    Parallel tracking and mapping for small ar workspaces. /
    Georg Klein and David Murray. //
    In Proceedings of the 2007 6th IEEE and ACM International Symposium on Mixed and Augmented Reality,
    ISMAR ’07, pages 1–10, Washington, DC, USA, 2007. IEEE Computer Society.

    \bibitem{sift-paper}
    Distinctive image features from scale-invariant keypoints. /
    David G. Lowe. //
    Int. J. Comput. Vision, 60(2):91–110, November 2004.

    \bibitem{surf-paper}
    Speeded-up robust features (surf) /
    Herbert Bay, Andreas Ess, Tinne Tuytelaars, and Luc Van Gool. //
    Comput. Vis. Image Underst., 110(3):346–359, June 2008.

    \bibitem{fast-paper}
    Machine learning for high-speed corner detection. /
    Edward Rosten and Tom Drummond. //
    In Proceedings of the 9th European Conference on Computer Vision -
    Volume Part I, ECCV’06, pages 430–443, Berlin, Heidelberg, 2006. Springer-Verlag.

    \bibitem{orb-paper}
    Orb: An efficient alternative to sift or surf. /
    Ethan Rublee, Vincent Rabaud, Kurt Konolige, and Gary Bradski. //
    In Proceedings of the 2011 International Conference on Computer Vision,
    ICCV ’11, pages 2564–2571, Washington, DC, USA, 2011. IEEE Computer Society.

    \bibitem{brief-paper}
    Brief: Binary robust independent elementary features. /
    Michael Calonder, Vincent Lepetit, Christoph Strecha, and Pascal Fua. //
    In Proceedings of the 11th European Conference on Computer Vision:
    Part IV, ECCV’10, pages 778–792, Berlin, Heidelberg, 2010. Springer-Verlag.

    \bibitem{brisk-paper}
    Brisk: Binary robust invariant scalable keypoints. /
    Stefan Leutenegger, Margarita Chli, and Roland Y. Siegwart. //
    In Proceedings of the 2011 International Conference on Computer Vision,
    ICCV ’11, pages 2548–2555, Washington, DC, USA, 2011. IEEE Computer Society.

    \bibitem{theia-sfm}
    Theia multiview geometry library: Tutorial \& reference.
    [Electronic resource] / Chris Sweeney. - Mode of access: http://theia-sfm.org.
    - Date of access: March 2018.

    \bibitem{direct-methods}
    About direct methods. / Michal Irani and P. Anandan. //
    In Proceedings of the International Workshop on Vision Algorithms: Theory and Practice,
    ICCV ’99, pages 267–277, London, UK, UK, 2000. Springer-Verlag.

    \bibitem{DBLP:journals/corr/TatenoTLN17}
    CNN-SLAM: real-time dense monocular SLAM with learned depth prediction. /
    Keisuke Tateno, Federico Tombari, Iro Laina, and Nassir Navab. // CoRR, abs/1704.03489, 2017.

\end{thebibliography}
\endgroup
