\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\begin{document}

{\Large

\textbf{Writing assignment \#1}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{Compare yourself today and yourself five years ago. In what ways
are you the same or different?}

People change significantly with time. Remember any of your friends - you will
see how their behaviour or their values are different from those ten, five or
even a year ago. Comparing myself today with myself five years ago I have
noticed I became much more responsible and thoughtful although my core
worldviews remained unchanged.

Responsibility and thoughtfulness are the things which come with age and I can
see I made a huge progress here. You decide more and more things on
your own while the decisions your family makes about you become less relevant.
I am currently finishing my undergraduate studies and that is the time you
have to make a lot of serious decisions about your future career and your future
life. That is why my responsibility skills found a way for development and
that is how I had to become more thoughtful with time.

Despite of all the examples of how I am different from five years ago, I should
say my crucial worldviews have not really changed. I believe that is explained
with a statement that worldviews which we have from a deep childhood
will be in our minds through the whole life. That is an example of how our
parents and our entire family are forming our conscious. Your future friends
will certainly have a great impact on how your treat your surroundings but
this impact will never be as strong as the one from your childhood.

Nobody argues time has a great effect on people and although all the changes
are as influential as an amount of time passed, most internal beliefs are remained
unchanged through the lifetime. I have noticed a bunch of minor changes in myself
during the past five years, however, the general picture of the world is the same.

\subsection*{Some people prefer to play team sports, while others prefer to play
individual sports. Discuss the advantages of each. Indicate which you prefer
and why.}

People worldwide spend an essential amount of time playing sports. Some kind of
sports are for teams and some are for individuals. Each kind has its own
benefits: team sports develop communication skills as well as
physical while individual sports are a great way to reflect. As for me I prefer
team sports over individual as they help me spend time with my friends which
is an amazing source for motivation and self-confidence.

I was always treating team sports as being a part of a group and achieving the
goals together rather than a way to show your excellent physical skills.
Team sports make you think about yourself as about a part of something bigger.
Team sports teach you how to care not only about yourself but about each of
your teammates: you can not achieve anything unless you are a part of a group.
I believe these are the skills which are also useful in real world: studying,
having a job or even starting a family - all of these are accomplishments of
groups and that is the only way that can be done. Playing team
sports with your close friends rather then with random people gives you an
opportunity to spend time together with both fun and benefit.
I always find that very motivating and that is why I like doing team sports.

At the same time the benefit of individual sports is how they give you your
own time which is an amazing opportunity to do reflexion and thinking.
While doing some physical activity your mind is often out of any work. An example
here is swimming which I enjoy very much. While swimming and doing pretty simple
breathing and moving exercises you have time to do thinking about every thing
which bothers you: whether it is an upcoming deadline or a gift for your best
friend for birthday.

Individual and team sports are different from each other but each of them
has its own benefits. In my opinion the main advantage of team sports is
developing a skill of being a part of a group while individual sports are a
great source for thinking. I prefer team sports over individual as spending time
with friends while doing sports makes me feel more confident.

\end{document}
