\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\linespread{1.5}

\begin{document}

{\Large

\textbf{Writing assignment \#1}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{Compare yourself today and yourself five years ago. In what ways
are you the same or different?}

People change significantly with time. Remember any of your friends - you will
see how their behaviour or their values are different from those ten, five or
even a year ago. Comparing myself today with myself five years ago I have
noticed I became much more responsible and thoughtful although my core
worldviews remained unchanged.

Responsibility and thoughtfulness are the things which come with age and I can
see I made a huge progress here. You decide more and more things on
your own while the decisions your family makes about you become less relevant.
I am currently finishing my undergraduate studies and that is the time you
have to make a lot of serious decisions about your future career and your future
life. That is why my responsibility skills found a way for development and
that is how I had to become more thoughtful with time.

Despite of all the examples of how I am different from five years ago, I should
say my crucial worldviews have not really changed. I believe that is explained
with a statement that worldviews which we have from a deep childhood
will be in our minds through the whole life. That is an example of how our
parents and our entire family are forming our conscious. Your future friends
will certainly have a great impact on how your treat your surroundings but
this impact will never be as strong as the one from your childhood.

Nobody argues time has a great effect on people and although all the changes
are as influential as an amount of time passed, most internal beliefs are remained
unchanged through the lifetime. I have noticed a bunch of minor changes in myself
during the past five years, however, the general picture of the world is the same.

\vspace{15mm}

Total number of words: 298.

\end{document}
