\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\linespread{1.5}

\begin{document}

{\Large

\textbf{Writing assignment \#3}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{Drug abuse has become a major social problem in many parts of the
world. Discuss the consequences of drug abuse and ways to deal with the problem}

The world has faced a lot of social problems recently. Poverty, hunger, ecological
problems are threatening normal life of humanity. Drug abuse is considered to be one
of the major problems in a modern world and it must be fought accordingly.

Drug abuse damages health irreversibly and in many cases leads to death of
the one who is addictive. Drug abuse will not be such an important problem
to deal with if it does not cause permanent health problems. It influences all
parts of human's body, from brain to blood system. The one who is on an early
stage of the abuse might simply look pale and feel weak. With abuse developing
people become unable to work, they are out of the society and they are facing
serious issues with health. Unless the one is helped, drug abuse might end lethally.

Drug abuse should be prevented both by blocking access to drugs and by running
programs of rehabilitation and integrating affected back to society.
Making drugs unaccessible will lead to most people not being able to even try
them: that is the first step to prevent addiction. At the same time it is
impossible to remove drugs from the society completely which means that
people who were unlucky to face with drugs should have a proper way to return back
to normal life.

Drug abuse is one of the most essential problems in a modern world, which makes
a lot of people loose their health, families and jobs and it should be fought
on every stage of its development.

\vspace{15mm}

Total number of words: 259.

\end{document}
