\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\linespread{1.5}

\begin{document}

{\Large

\textbf{Writing assignment \#2}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{Compare and contrast your way of life with that of your parents.
Whose way of life do you think would be more satisfying for future generations?}

Any society consists of people of various ages. People of different ages have
their own beliefs, worldviews and goals in life.
People of older generations have established views on things and are more experienced
while youth are in the age of forming their conscious and are much more curious.

As I see it people of an older generation have their strong opinion on most of
the processes going around and therefore are not accepting any new ideas easily.
That seems to be a natural thing for me: when you are rather old than young you have seen
and have felt enough to form a complete worldview. Beliefs which were essential
in young age remain being essential through the whole life. That is how generation gap
appears: mature people can not understand the life of youth while young people
are completely unfamiliar with what is valuable for older people. Memories about
young ages are so vital that fear of losing it blocks from accepting new.

In the same time young people are in process of forming their conscious, they are
curious about the world, they think critically and ready to learn. This is achieved
by not having any stereotypes or preconceptions. Young people are more willing
to share and accept, they are more likely to take a risk and potentially get into trouble
in order to try something new. That is how great inventions and discoveries are made
and that is how innovations appear in the world.

People of older generations have much more experience and therefore might
understand some concepts better while young people are more likely to accept new ideas
and to learn. My personal opinion is that actions of youth are always
more satisfying for future generations as they bring innovations and fresh ideas
into the world.

\vspace{15mm}

Total number of words: 299.

\end{document}
