\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\linespread{1.5}

\begin{document}

{\Large

\textbf{Writing assignment \#5}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{Plants can provide food, shelter, clothing or medicine. What is
one plant that is important to you and to people in your country?
Use specific reasons}

Plants are an essential part of nature where everything is related to each other.
Humans are not least vital part of it and they have a long history of relations with
plants since the times when plants provided people with shelter, clothing and food
till today when we all enjoy going to nature to have a rest of a busy city life.
That is doubtless every single kind of plants has its own role in nature and none
is less important than others. However I would name a cornflower to have a special role
in belarusian culture and to be especially valuable for people in my country and
for me personally for its beauty, simpleness and symbolism.

The first reason for a cornflower to be that special is how beautiful and, at the
same time, how simple it is. It does not need any extra conditions to be grown
and you can easily find it in a forest or in a field. Cornflower bouquets are
often sold on Minsk's streets and, in my opinion, look much more intriguing than
roses or other flowers normally considered to be the most beautiful.

The second reason is that cornflower has its value as a brand of the country.
You can often find a cornflower on tourist information booklets. A cornflower is
a symbol of the largest belarusian airline company. A cornflower may be often
found on billboards encouraging to protect the nature.

A cornflower is a plant which is important for people in my country for its cultural
significance and its role in shaping country's brand. I also find a cornflower
very important and not only for its relations with the culture but for simpleness
and pure beauty.

\vspace{15mm}

Total number of words: 285.

\end{document}
