\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{indentfirst}
\pagenumbering{gobble}

\linespread{1.5}

\begin{document}

{\Large

\textbf{Writing assignment \#6}

Uladzislau Bohdan

}

\vspace{10mm}

\subsection*{It is generally agreed that society benefits from the work of its
members. Compare the contribution of artists to society with the contribution of
scientists to society. Which type of contributions do you think is valued more
by your society?}

As I see it, society not only benefits but is defined by the work of its members.
Every small contribution and every interaction between members makes changes
into society and improves it in a particular way. From my point of view,
the contribution of artists, scientists or any other groups of people in my society are equally
significant and each member is equally valueable.

The reason I believe artists' contribution to the society is significant is
because they improve cultural life and help people to spend time with joy.
Artists is a suprizingly large group of people and among others it includes signers and
painters, moviemakers and designers. Realizing how diverse the group of artists is gives us
an understanding, that every time we are going out, either to a cinema or
to some sort of an exhibition, we enjoy the work of artistic part of the society
and that proves how significant their role is.

Scientists change our lifes in a slightly different way, they are consistently
improving the ways we are dealing with daily routine, which is not less significant
as the contribution of artists. We can see the results of scientists' work everywhere:
they improve the way of how we communicate, commute or make payments, they bring
improvements into our houses and on the streets. Each small contribution, even if not
instantly noticable, results into making routine operations we perform more comfortable.

I believe that contributions of each member of my society, whether we are talking
about an artist or a scientist, are equally important and these contributions work
both ways: scientists benefit from the work of artists and vice versa and that
is, in the end, how society benefits in general.

\vspace{15mm}

Total number of words: 285.

\end{document}
